% Norma citácii: ISO 690

\def\bibname{Bibliography}
\begin{thebibliography}{99}
	\addcontentsline{toc}{chapter}{\bibname}

%% Theory
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\bibitem{tisza}
	{\sc Tisza, L.}
	\emph{The viscosity of liquid helium and the Bose-Einstein statistics.}\\
	Comptes Rendus Acad. Sciences, \textbf{207}:1186-1189 (1952)

	\bibitem{landau}
	{\sc Landau, L.D.}
	\emph{The theory of superfluidity of helium II}\\
	J. Phys. USSR, Vol. \textbf{11}, 91 (1947)

	\bibitem{vortex_ring}
	{\sc Rayfield, G.W., Reif F.}
	\emph{Quantized Vortex Rings in Superfluid Helium} Phys. Rev. A, \textbf{136}, 5A (1964)

	\bibitem{feynman}
	{\sc Feynman, R.}
	\emph{Application of quantum mechanics to liquid helium}.\\
	Prog. in Low Temp. Phys., \textbf{1}, 17-53 (1955)

	\bibitem{onsager}
	{\sc Penrose, O., Onsager, L.}
	\emph{Bose-Einstein condensation and liquid helium}.\\
	Phys. Rev., \textbf{104}, 576 (1956)

	\bibitem{vinen}
	{\sc Vinen, W.F.} and {\sc Hall, H.E.}
	\emph{The theory of mutual friction in uniformly rotating helium II}.
	Proc. Royal Soc. London 238 (1957) 204

	\bibitem{donnelly}
	{\sc Donnelly, R.J., Barenghi, C.F}
	\emph{The Observed Properties of Liquid Helium at the Saturated Vapor Pressure}. American Ins. of Phys. and Chem. Soc. (1998)

	\bibitem{roberts}
	{\sc Roberts, P.H.}
	\emph{} Phys. Rev. A, 55 (1971)

	\bibitem{donnelly_book}
	{\sc Donnelly, R.J.}
	\emph{Quantized Vortices in Helium II}.\\
	Cambridge studies in low temp. phys. (2005)

	\bibitem{osborne}
	{\sc Osborne, D.V.}
	\emph{The Rotation of Liquid Helium-II}.\\
	Proc. Royal Soc. London , \textbf{63}: 909-912 (1950)

	\bibitem{laminar-turbulence}
	{\sc Van Dyke, M.}
	\emph{An Album of Fluid Motion}.\\
	The Parabolic Press, Stanford, California (1982). ISBN 0-915760-02-9

	\bibitem{barenghi}
	{\sc Barenghi, F.}
	\emph{Superfluid vortices and Turbulence}. Quantized Vortex Dynamics and Superfluid Turbulence, Chap.1 (2001)

	\bibitem{bakalaris}
	{\sc Bahyl, J.}
	\emph{Measurement of Quantum Turbulence in Superfluid Helium Using Second Sound Attenuation}.
	Bachelor Thesis, FMPH UK, Bratislava (2016)

	\bibitem{stokes}
	{\sc Schmoranzer, D., Kráľová, V., et al.}
	\emph{}	Phys. Rev. E, 81 (2010)

	\bibitem{universal_scaling}
	{\sc Jackson, M.J., Schmoranzer, D., et al.}
	\emph{Universal Drag Force Scaling in High Stokes Number Oscillatory Flows of He II}. Phys Rev B, \textbf{submitted} (2018)

	\bibitem{crit-velocity}
	{\sc Nichol, H.A., Skrbek, L. et al.}
	\emph{} Phys. Rev. Lett. \textbf{92} (2004).

%% Experiments
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	\bibitem{skyba}
	{\sc Holt, S., Skyba, P.}
	\emph{} Rev. Sci. Instrum., \textbf{83} (2012)

	\bibitem{wire}
	{\sc Guénault, A.M., Kennedy, S.G., et al.}
	\emph{} J, of Low Temp Phys., \textbf{62} (1986)

	\bibitem{forks}
	{\sc Blaauwgeers, R. Blažková, M.} \text{and col.}
	\emph{Quartz tuning fork: Thermometer, Pressure- and Viscometer for Helium Liquids} J. of Low Temp Phys., Vol. \textbf{146} (2007)

	\bibitem{fork-exp}
	{\sc Bradley, D.I., Človečko, M.} \text{and col.}
	\emph{} Phys. Rev. B \textbf{85} (2012)

	\bibitem{multiple-vels}
	{\sc Schmoranzer, D., Jackson. M.J., et al.}
	\emph{Multiple critical velocities in oscillatory flow of superfluid $\He$ due to quartz tuning forks}.
	Phys. Rev. B \textbf{94} (2010)

	\bibitem{svoc2016}
	{\sc Bahyl, J.}
	\emph{Measurement of quantum turbulence in superfluid He-4}.
	Student conference, FMPH UK, Bratislava (2016)

%% Simulations
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	\bibitem{schwarz}
	{\sc Schwarz, K.W.}
	\emph{Three-dimensional vortex dynamics in superfuid He 4: Homogeneous superfluid turbulence}\\
	Phys Rev B, Vol. \textbf{38}, 4 (1988)

	\bibitem{tsubota}
	{\sc Tsubota, M., Fujimoto, K., Yui S.}
	\emph{Numerical Studies of Quantum Turbulence}.\\
	Journal of Low Temp Phys, 188 (2017)

	\bibitem{FDclosed}
	{\sc Baggaley, A.W., Barenghi, C.F.}
	\emph{Spectrum of turbulent Kelvin-waves cascade in superfluid helium}.\\
	Phys Rev B, Vol. \textbf{83}, 4 (2011)

	\bibitem{samuels}
	{\sc Samuels, D.C.}
	\emph{Superfluid vortices and Turbulence}. Quantized Vortex Dynamics and Superfluid Turbulence, Chap.9 (2001)

	\bibitem{element}
	{\sc Documentation}
	\emph{http://docs.desktop.aero/appliedaero/potential3d/BiotSavart.html}

	\bibitem{tree_alg}
	{\sc Baggaley, A.W., Barenghi, C.F.}
	\emph{Tree Method for Quantum Vortex Dynamics}. Journal of Low Temp Phys, 166 (2012)

	\bibitem{barnes}
	{\sc Barnes, J., Hut, P.}
	\emph{A hierarchical O(N log N) force-calculation algorithm}. Nature, \textbf{324}, 446 (1986)

%% Results
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	\bibitem{optical_exps}
	{\sc Bradley, D.I., Crookston, P., et al.}
	\emph{} J. of Low Temp. Phys., \textbf{161}, 536 (2010)

	\bibitem{scaling_function}
	{\sc Ekinci, K.L., Yakhot, V., et al.}
	\emph{} Lab Chip, \textbf{10}, 3013 (2010)



\end{thebibliography}
