% Norma citácii: ISO 690

\def\bibname{Bibliography}
\begin{thebibliography}{99}
	\addcontentsline{toc}{chapter}{\bibname}

\bibitem{kapitsa}
{\sc Kapitsa, P.}
\emph{The Super-Fluidity of Liquid Helium II}.
Nature \textbf{141}, 74 (1938)

\bibitem{tong}
{\sc Tong, D.}
\emph{Statistical physics}.
University of Cambridge Part II

\bibitem{tisza}
{\sc Tisza, L.}
\emph{The viscosity of liquid helium and the Bose-Einstein statistics.}\\
Comptes Rendus Acad. Sciences, \textbf{207}:1186-1189 (1952)

\bibitem{landau}
{\sc Landau, L.D.} \text{and} {\sc Lifshitz, E.M.}
\emph{Fluid Mechanics}, Second English Edition.\\
Pergamon Books Ltd., (1987). \mbox{ISBN~0-08-033933-6}

\bibitem{landau_superfluid}
{\sc Landau, L.D.}
\emph{The theory of superfluidity of helium II}.\\
J. Phys. USSR, Vol. \textbf{11}, 91 (1947)

\bibitem{andro}
{\sc Andronikashvili, E.L.}
J. Phys. USSR, \textbf{10}, 201 (1946)

\bibitem{skrbek}
{\sc Skrbek, L.} et al.
\emph{Fyzika nízkých teplot}, 1. vydání.\\
Praha: {\sl MatfyzPress}, (2011). \mbox{ISBN~978-80-7378-168-2}.

\bibitem{varga}
{\sc Varga, E.}
\emph{Second sound as a tool to study He-II flow}.
Bachelor thesis (2012).

\bibitem{osborne}
{\sc Osborne, D.V.}
\emph{The Rotation of Liquid Helium-II}.
Proc. Royal Soc. London , \textbf{63}: 909-912 (1950)

\bibitem{feynman}
{\sc Feynman, R.}.
\emph{Application of quantum mechanics to liquid helium}.\\
Progress in Low Temperature Physics, \textbf{1}, 17-53 (1957)

\bibitem{tony}
{\sc Guénault, T.}
\emph{Basic Superfluids}.\\
Taylor $\&$ Francis e-Library (2003). ISBN~0-203-26973-X.

\bibitem{vinen1}
{\sc Vinen, W.F.} and {\sc Hall, H.E.}
\emph{The rotation of liquid helium II}

I.\hspace{2mm}\emph{Experiments on the propagation of second sound in uniformly rotating helium II}.

Proc. Royal Soc. London \textbf{238}:204-214 (1957)

\bibitem{vinen2}
{\sc Vinen, W.F.} and {\sc Hall, H.E.}
\emph{The rotation of liquid helium II}

II.\hspace{2mm}\emph{The theory of mutual friction in uniformly rotating helium II}.

Proc. Royal Soc. London \textbf{238}:215-234 (1957)

\bibitem{physrevB}
{\sc S. Babuin , M. Stammeier, E. Varga, M. Rotter, L. Skrbek  }
\emph{Quantum turbulence of bellows-driven $\He$ superflow: Steady state} Phys. Rev. B, \textbf{86} (2012)

\bibitem{turbulence}
{\sc Van Dyke, M.}
\emph{An Album of Fluid Motion}.\\
The Parabolic Press, Stanford, California (1982). ISBN 0-915760-02-9

\bibitem{schoepe}
{\sc R. Hänninen, W. Schoepe}
\emph{Dynamical Scaling of the Critical Velocity for the Onset of Turbulence in Oscillatory Superflows}.
J. Low Temp. Phys. \textbf{164}: 1-4 (2011)

\bibitem{forks}
{\sc R. Blaauwgeers} \text{and col.}
\emph{Quartz tuning fork: Thermometer, Pressure- and Viscometer for Helium Liquids} Journal of low. temp. phys., Vol. \textbf{146}, (2007)

\bibitem{acoustic}
{\sc R.I. Bradleys, D. Schmoranzer} \text{and col.}
\emph{Crossover from hydrodynamic to acoustic drag on quartz tuning forks in normal and superfluid $ \He $}. Phys. Rev. B, \textbf{85} (2012)

\bibitem{donnelly}
{\sc Donnelly, R.J., Barenghi, C.F}
\emph{The Observed Properties of Liquid Helium at the Saturated Vapor Pressure}. American Ins. of Phys. and Chem. Soc. (1998)

\bibitem{lancaster}
{\sc Ahlstorm, S.L., Brandley, D.I.} \text{and col.}.
\emph{Frequency-dependent drag from quantum turbulence produced by quartz tuning forks in superfluid $ \He $}.
Phys. Rev. B, \textbf{89} (2014)

\bibitem{history}
{\sc Brandley, D.I., Guénault, A.M.} \text{and col.}
\emph{History Dependence of Turbulence Generated by a Vibrating Wire in Superfluid $ \He $ at $ 1.5\unit{K} $}.\\
J. Low Temp. Phys. \textbf{162}:375-382 (2011)

\bibitem{Emilfluids}
{\sc Varga, E., Babuin, S., Skrbek, L.}
\emph{Second-sound studies of coflow and counterflow of superfluid $ \He $ in channels}.
Physics of fluids \textbf{27} (2015)

\bibitem{opticalfork}
{\sc Bradley, D.I., Crookston, P.} \text{and col.}
\emph{Measuring the Prong Velocity of Quartz Tuning Forks Used to Probe Quantum Fluids}.
J. Low Temp. Phys. \textbf{161}:536-547 (2010)

\bibitem{PraguePRB}
{\sc Blažková, M., Schmoranzer, D.} \text{and col.}
\emph{Generation of turbulence by vibrating forks and other structures in superfluid $ \He $}.
Phys. Rev. B, \textbf{79} (2009)

\bibitem{jackson}
{\sc Jackson, M.J.} \text{and col.}
\emph{Measurement of Vortex Line Density Generated by a Quartz Tuning Fork in Superfluid $ \He $}
J. Low Temp. Phys. \textbf{183}:208-214 (2016)

\bibitem{bahyl}
{\sc Bahyl, J.}
\emph{Measurement of quantum turbulence in superfluid $ \He $}.
FMFI ŠVK (2016)



\end{thebibliography}
